The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-17 article.tex
added model 5 to first table - changed covariates

\begin{table}[]
\caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}ccccc@{}}
    \toprule
    & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
    \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\
    {1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 4} & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\
        Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}
    \end{tabular}}
\end{table}

>>>>

\begin{table}[]
\caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}ccccc@{}}
    \toprule
    & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
    \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A\\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 4} & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\
        \\ \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope One Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}
        \\
        \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
     \textbf{Model 5} & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year * Region\end{tabular}
        \end{tabular}}
\end{table}
